---
title: "High Sensitivity Troponin"
author: "Ashley Snyder"
date: "April 5, 2018"
output: 
  html_document:
    toc: true
    toc_depth: 3
    theme: united  # many options for theme, this one is my favorite.
---

```{r setup, include=FALSE}
setwd("/Users/msis/Box Sync/MPrOVE Files/Projects/Chest Pain/")
knitr::opts_chunk$set(echo = TRUE)
```


# Study Objectives

1. To determine the characteristics of patients getting the high sensitivity troponing (hsTrop) test in the ED, excluding patients who are part of the chest pain cohort

2. To assess the downstream impact of the hsTrop on ordering practices for patients not included in the chest pain cohort



```{r, include=FALSE}
library(tidyverse)
library(readxl)
library(pastecs)
setwd("/Users/msis/Box Sync/MPrOVE/Chest Pain Pathway/Data")
allpatients <- read_excel("hstrop.xlsx", sheet = "Data")
names(allpatients)[names(allpatients) == 'hstrop'] <- 'High Sensitivity Troponin'
names(allpatients)[names(allpatients) == 'chest_pain_pt_flag'] <- 'Chest Pain Pathway'
names(allpatients)[names(allpatients) == 'first_clin_imp'] <- 'First Clinical Impressions'
names(allpatients)[names(allpatients) == 'hosp_dispo'] <- 'Hospital Discharge Disposition'
names(allpatients)[names(allpatients) == 'har_final_1st_disch_dx'] <- 'Discharge Diagnosis'

#Only patients with hstrop drawn
hstrop = filter(allpatients, `High Sensitivity Troponin`==1)

#Only patients who went through the chest pain pathway
cp = filter(allpatients, `Chest Pain Pathway`==1)

#Patients who had hstrop and NO chest pain pathway
hstrop.nocp = filter(hstrop, `Chest Pain Pathway`==0)
```

```{r ICD, echo=FALSE}
# Commenting this but try (after updating variables names):
#  allpatients = allpatients %>% 
#       mutate( first_clin_imp_icd10_3 = stringr::str_sub(first_clin_imp_icd10, 1, 3) )
# Then use this in the rollup.  If there is leading whitespace, use stringr::str_trim() first.

```

# Determining the Population

Cross-tabulation of patients who had a high sensitivity troponin drawn and those who went through the chest pain pathway


```{r, echo=FALSE}
tab = allpatients %>%
  group_by(`High Sensitivity Troponin`, `Chest Pain Pathway`) %>%
  summarize(n=n()) %>%
  mutate(percent=sprintf('%4.1f', 100*(n/sum(n) ) ))
tab %>% knitr::kable()
```

From above, there are **n=1,044** (59.9%) patients who recieved hsTrop but did not go through the chest pain pathway. These are the current patients of interest.

## Characterizing the Patient Population 


###First Clinical Impressions on Arrival to the ED


```{r, echo=FALSE}
tab2 = hstrop.nocp %>%
  group_by(`First Clinical Impressions`) %>%
  summarize(n=n()) %>%
  mutate(percent=sprintf('%4.1f', 100*(n/sum(n) ))) 
tab3 <- tab2[order(-rank(tab2$percent)), ]
#tab3 %>% knitr::kable()
tabl3 %>% DT::datable()
```

There is a lot of variation in admission diagnosis. Could we consider grouping these diagnoses into categories? 


###Hospital Discharge Disposition


```{r, echo=FALSE}
tab4 = hstrop.nocp %>%
  group_by(`Hospital Discharge Disposition`) %>%
  summarize(n=n()) %>%
  mutate(percent=sprintf('%4.1f', 100*(n/sum(n)) )) 
tab5 <- tab4[order(-rank(tab4$percent)), ]
#tab5 %>% knitr::kable()
tab5 %>% DT::datatable()
```


###Discharge Diagnosis


```{r, echo=FALSE}
tab4 = hstrop.nocp %>%
  group_by(`Discharge Diagnosis`) %>%
  summarize(n=n()) %>%
  mutate(percent=sprintf('%4.1f', 100*(n/sum(n)) )) 
tab5 <- tab4[order(-rank(tab4$percent)), ]
#tab5 %>% knitr::kable()
tab5 %>% DT::datatable()
```


